---
title: "Gun Control Chi Square"
author: "Daphne Virlar"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Daphne and I'm adding text to test whether or not Sidney can get this file form git.


I'm changing something in this file. It's still Daphne. Sidney is the Dancing Queen.

Daphne is young and sweet only 17. 





Creator (Daphne):

Gitting gc_df.csv data, loading the tidyverse, and getting summary counts. 

```{r}

library(tidyverse)

gc_df <- read_csv("gc_df.csv")
View(gc_df)


#Remove NA values
get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% #Create contingency column of counts
  count(gender, make_get_guns) %>%  #As is, table is in long format. We want it in WIDE format.
  spread(make_get_guns, n) %>% #remove gender column. First row female, second male
  select(-gender)

#change row names
rownames(get_guns) <- c("Female", "Male")

```

I'm the collaborator Sidney the Dancing Queen and I am going to do chi-square

Question for the data:
Is there an association between sex and the opinion of level of difficulty of obtatining a gun? (Gun controll recommendation)

Is perception of gun control access independent of sex?

Chi-Square
```{r}
#table of proportions by row
gun_prop <- prop.table(as.matrix(get_guns), 1) #this gets the proportion for the total for the table, want proportions with in rows.. add (, 1) at the end

gun_prop


#perform chi-square
#x is the chi, different than x. be sure to have symbol in markdown
guns_x2 <- chisq.test(get_guns)
guns_x2


```

Recommended gvmt action on gun access differs significatly for males and females ($\chi^2$(`r guns_x2$parameter`) = ...., p < 0.001)

not enough info for the audiance!!! give more values, say differences, and such. 
